Comparing Power Optimizations in the Reorder Buffer

### 2011-06-08 paper/paper.tex
Background info on dynamic buffer.

Upon execution completion, the output value is stored in the ROB with its 
corresponding entry and that entry is marked as valid or completed with a 
1 bit flag.  An entry is committed from the ROB to the architectural register
file (ARF) when that entry is the oldest (lowest PC) and its result has been 
marked as valid. 
\subsection{Circular ROB}
The circular ROB is one of the most basic implementations of the ROB.  Simply using
a circular buffer as the structure to hold each entry.  Since the ROB is basically
just memory, there are two special slots for to keep track of the head and tail
pointer to create the circular buffer.  As entries are written into the ROB, the
entry is written at the tail pointer and then the tail pointer is incremented.
Likewise when an entries is written to the ARF, the head pointer is incremented.
The circular buffer method is widely used since it inherently keeps track of the 
oldest instruction (which is at the head pointer), as well as which entry slots
are used or empty.   However it may not be very power efficient if there is a large
number of empty slots at any given point of the execution.    
\subsection{Dynamic ROB}

>>>>

Upon execution completion, the output value is stored in the ROB with its 
corresponding entry and that entry is marked as valid or completed with a 
1 bit flag.  An entry is committed from the ROB to the architectural register
file (ARF) when that entry is the oldest (lowest PC) and its result has been 
marked as valid. 
\subsection{Circular ROB}
The circular ROB is one of the most basic implementations of the ROB.  Simply using
a circular buffer as the structure to hold each entry.  Since the ROB is basically
just memory, there are two special slots for to keep track of the head and tail
pointer to create the circular buffer.  As entries are written into the ROB, the
entry is written at the tail pointer and then the tail pointer is incremented.
Likewise when an entries is written to the ARF, the head pointer is incremented.
The circular buffer method is widely used since it inherently keeps track of the 
oldest instruction (which is at the head pointer), as well as which entry slots
are used or empty.   However it may not be very power efficient if there is a large
number of empty slots at any given point of the execution.    
\subsection{Dynamic ROB}
The dynamic ROB aims to reduce power by turning off portions of the buffer when they
are not needed, and turning them back on when they become necessary. By partitioning
the buffer into what is essentially smaller buffers, the complexity of each partition
is reduced. Further, the ROB will then be custom sized to need, thus reducing energy
wasted powering large stretches of empty entries. Due to the large percentage of energy
consumption stemming from leakage power, turning off partitions contribute significant
power savings over the base circular ROB.
